Supplementary Content

### 2025-01-04 Writeup/plos/appendix/Appendix.tex
plos1submission

\title{Supplementary Content}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Understanding the role of different proxy selection methods in
High-Dimensional Propensity Score Framework - A Plasmode simulation
study}
\author{}
\date{\vspace{-2.5em}}

@@

\section{True outcome model for Plasmode Simulation Data
Generation}\label{true-outcome-model-for-plasmode-simulation-data-generation}

@@

\section{SE comparison}\label{se-comparison}

\textcolor{red}{*need to have a brief description of these figures.*}

>>>>

\title{Supplementary Content}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Is There a Competitive Advantage to Using Multivariate
Statistical or Machine Learning Methods Over the Bross Formula in the
hdPS Framework for Bias and Variance Estimation?}
\author{}
\date{\vspace{-2.5em}}

@@

\section{True Outcome Model for Plasmode Simulation Data
Generation}\label{true-outcome-model-for-plasmode-simulation-data-generation}

@@

\section{Standard Error comparison}\label{standard-error-comparison}
